Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-02 paper/paper.Rmd
prepare custom cv

```{r buffer, fig.cap="Visualization of the 'Spatial buffering' method from package `blockCV`.", out.width="40%", fig.pos="ht"}
resampling_buffer = rsmp("spcv_buffer", theRange = 1000)
resampling_buffer$instantiate(task)

@@

```{r custom-cv,  fig.cap="Environmental blocking using a single predictor.", out.width="40%", fig.pos="ht", eval=FALSE}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

resampling_custom = rsmp("custom_cv")
resampling_custom$instantiate(task, split = zclass)
```

>>>>

```{r buffer, fig.cap="Visualization of the 'Spatial buffering' method from package `blockCV`.", out.width="40%", fig.pos="ht"}
task = tsk("ecuador")
resampling_buffer = rsmp("spcv_buffer", theRange = 1000)
resampling_buffer$instantiate(task)

@@

```{r custom-cv,  fig.cap="Custom resampling using an external factor vector.", out.width="40%", fig.pos="ht", eval=FALSE}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

resampling_custom = rsmp("custom_cv")
resampling_custom$instantiate(task, f = zclass)

autoplot(resampling_custom,
  size = 0.8, fold_id = 1, task = task) *
  ggplot2::scale_y_continuous(breaks = seq(-3.97, -4, -0.01)) *
  ggplot2::scale_x_continuous(breaks = seq(-79.06, -79.08, -0.01))
```
